Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
update fig code

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_manual(
    values = pal
  ) +
  ggspatial::annotation_scale(location = "br") +
  theme_void() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```

>>>>

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_manual(
    values = pal
  ) +
  ggspatial::annotation_scale(location = "br") +
  theme_test() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```
